---
title: Summary Reports for Sections, Divisions, and Functional Groups for the Maritimes Region.
author: " "
output:
  html_document:
    theme: flatly
    always_allow_html: true
  pdf_document: default
---

<span style="color:#43C6DB">As a manager,I want a summary reproducible report (PDF or Word). The report should serve as the authoritative source, providing a quarterly snapshot of MAR Science projects in a newsletter-like format.  The report will be ordered into the five functions of science (Monitoring, Research, Assessment, Data Management, and Other). The report can be created by filtering by theme, functional groups, section, or Division. The Marine Spatial Planning and Conservation Theme will be used for the pilot report. This reproducible reports will facilitate PIs in validating projects and managers recommend and approve proposed projects. </span>

## Select relevant tab for summary reports for the Maritimes Region {.tabset}

### Theme
```{r, echo=FALSE}
library(stringr)
library(dataSPA)

# NOTE: NEED TO DEFINE COOKIE FOR THIS TO WORK
if(!exists("cookie")){
  res <- try(load('../../../../Code (Not for GitHub)/10_landing_page/cookie'), silent=TRUE)
}
if (!(exists("cookie"))) {
      stop("Must add a line of code above that defines your cookie.")
}

if(!exists("om")){
  om <- getData(type="om", cookie=cookie, age=90)
  om <- om[which(str_trim(str_extract(om$section_display, "[^-]+")) == "Maritimes"),] # Hard coded in for maritimes
}

theme <- unique(om$theme)
theme <- theme[-which(theme == "0")]
d <- data.frame(matrix(NA, ncol = 1, nrow = length(theme)))
names(d) <- "Theme"
path <- "themes/"
links <- paste0(path, gsub(" ", "%20", theme),".html")
d$Theme <- paste0('<a href="',links,'">',theme,'</a>')

DT::datatable(d,
              caption = 'Table 1: Table linking each theme to a summary report',
              filter="top",
              escape=FALSE)
```

### Functional Group

```{r, echo=FALSE}
functional <- unique(om$functional_group)
functional <- functional[-which(functional == ""|functional == "0")]
df <- data.frame(matrix(NA, ncol = 1, nrow = length(functional)))
names(df) <- "Functional Group"
#df$`Functional Group` <- functional


path <- "functionalGroup/"
links <- paste0(path, gsub(" ", "%20", functional),".html")
df$`Functional Group` <- paste0('<a href="',links,'">',functional,'</a>')

ids <- vector(mode="list", length(functional))
for (i in seq_along(functional)) {
ids[i] <- paste0(unique(om$project_id[which(om$functional_group == functional[i])]), collapse=",")
}

DT::datatable(df,
              caption = 'Table 2: Table linking each functional group to a summary report',
              filter="top",
              escape=FALSE)
```



### Division

```{r, echo=FALSE}
divisions <- NULL
for (i in seq_along(om$section_display)) {
  divisions[[i]] <- strsplit(om$section_display[i], " - ", fixed=TRUE)[[1]][3]
}
divisions <- unique(divisions)

df3 <- data.frame(matrix(NA, ncol = 1, nrow = length(divisions)))
names(df3) <- "Division"

path <- "divisions/"
links <- paste0(path, gsub(" ", "%20", divisions),".html")
df3$Division <- paste0('<a href="',links,'">',divisions,'</a>')

DT::datatable(df3,
              caption = 'Table 4: Table linking each Division to a summary report',
              filter="top",
              escape=FALSE)
```


### Section

```{r, echo=FALSE}
sections <- unique(gsub(".*- ","",unique(om$section_display)))
if ("Aquatic Biotechnology Laboratory ( TO BE DELETE)" %in% sections) {
sections <- sections[-which(sections == "Aquatic Biotechnology Laboratory ( TO BE DELETE)")]
}

df2 <- data.frame(matrix(NA, ncol = 1, nrow = length(sections)))
names(df2) <- "Section"

path <- "sections/"
links <- paste0(path, gsub(" ", "%20", sections),".html")
df2$Section <- paste0('<a href="',links,'">',sections,'</a>')

DT::datatable(df2,
              caption = 'Table 3: Table linking each Section to a summary report',
              filter="top",
              escape=FALSE)

```


## {-}
